---
title: "R Notebook"
output:
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
  pdf_notebook: default
---

HW03 
Name:Beili LI
GTid:903461609

1.import data set 
```{r}
rm(list=ls())
#import data 
stock_data <- read.table("~/OneDrive - Georgia Institute of Technology/2020spring/ISYE6783-financial data analysis/Homework/HW3/m_logret_10stocks.txt",header=T)
head(round(stock_data[2:11],4))
attach(stock_data)
```
```{r}

sp500_blii=read.table("~/OneDrive - Georgia Institute of Technology/2020spring/ISYE6783-financial data analysis/Homework/HW3/m_sp500ret_3mtcm.txt",sep="",skip = 1,header = T)

head(round(sp500_blii[2:3],4))
attach(sp500_blii)
```
```{r}
#compute for log return 
aapl=AAPL-X3mTCM/(100*12) #monthly return for T-blii
adbe=ADBE-X3mTCM/(100*12)
adp= ADP-X3mTCM/(100*12)
amd= AMD-X3mTCM/(100*12)
dell= DELL-X3mTCM/(100*12)
gtw= GTW-X3mTCM/(100*12)
hp= HP-X3mTCM/(100*12)
ibm= IBM-X3mTCM/(100*12)
msft= MSFT-X3mTCM/(100*12)
orcl= ORCL-X3mTCM/(100*12)
log_sp=sp500-X3mTCM/(100*12)

```
2.fit linear model for 10 stocks and calculate the 0.95 CI fo intercept and slope
```{r}
#fit linear regression model for 10 stocks
#1----------------------------------------------
#fit linear regression model for stock AAPL
lm.aapl=lm(aapl~log_sp)
summary(lm.aapl)

#calclute the 95% CI for intercept and slope
confint(lm.aapl,level = 0.95)
```

```{r}
#2----------------------------------------------

#fit linear regression model for stock ADBE
lm.adbe=lm(adbe~log_sp)
summary(lm.adbe)

#calclute the 95% CI for intercept and slope
confint(lm.adbe,level = 0.95)
```

```{r}
#3----------------------------------------------
#fit linear regression model for stock ADP
lm.adp=lm(adp~log_sp)
summary(lm.adp)

#calclute the 95% CI for intercept and slope
confint(lm.adp,level = 0.95)
```
```{r}
#4----------------------------------------------
#fit linear regression model for stock AMD
lm.amd=lm(amd~log_sp)
summary(lm.amd)  
  
#calclute the 95% CI for intercept and slope
confint(lm.amd,level = 0.95)
```
```{r}
#5----------------------------------------------
#fit linear regression model for stock DELL
lm.dell=lm(dell~log_sp)
summary(lm.dell) 

#calclute the 95% CI for intercept and slope
confint(lm.dell,level = 0.95)
```
```{r}
#6----------------------------------------------
  
#fit linear regression model for stock GTW
lm.gtw=lm(gtw~log_sp)
summary(lm.gtw) 

#calclute the 95% CI for intercept and slope
confint(lm.gtw,level = 0.95)
```
```{r}
#7----------------------------------------------
  
#fit linear regression model for stock HP
lm.hp=lm(hp~log_sp)
summary(lm.hp) 

#calclute the 95% CI for intercept and slope
confint(lm.hp,level = 0.95)
```
```{r}
#8----------------------------------------------
  
#fit linear regression model for stock IBM
lm.ibm=lm(ibm~log_sp)
summary(lm.ibm) 

#calclute the 95% CI for intercept and slope
confint(lm.ibm,level = 0.95)
```
```{r}
#9----------------------------------------------
  
#fit linear regression model for stock MSFT
lm.msft=lm(msft~log_sp)
summary(lm.msft) 

#calclute the 95% CI for intercept and slope
confint(lm.msft,level = 0.95)
```
```{r}
#10----------------------------------------------
  
#fit linear regression model for stock ORCL
lm.orcl=lm(orcl~log_sp)
summary(lm.orcl) 

#calclute the 95% CI for intercept and slope
confint(lm.orcl,level = 0.95)


```
(3)From the above result we can see that other p-values, except DELL, for intercept term in 10 regression models are biger than 0.05 so we accept the H0:aj=0. There is no intercept term for 9 models and no significant evidence against CAPM here. 

For Dell the p-value is 0.032 so we reject the H0,  aj is not equal to 0. 


